Loop-Aware Optimizations in PyPy's Tracing JIT

### 2012-08-17 talk/dls2012/paper.tex

The Python interpreter of the RPython framework is a complete Python
version 2.7 compatible interpreter. A set of numerical
calculations were implemented in both Python, C and Lua and their
runtimes are compared in Figure~\ref{fig:benchmarks}.\footnote{
    The benchmarks and the scripts to run them can be found in the repository for this paper:
    \texttt{https://bitbucket.org/pypy/extradoc/src/ tip/talk/dls2012/benchmarks}
}
For benchmarks using larger Python applications the times are unaffected or
slightly improved by the loop optimization of this paper.

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{benchmarks/result.pdf}
\label{fig:benchmarks_plot}
\caption{Benchmark results normalized with the runtime of the C version. The CPython results have been omitted to make the plot readable.}
\end{center}
\end{figure}

The Python interpreter of the RPython framework is a complete Python
version 2.7 compatible interpreter. A set of numerical
calculations were implemented in both Python, C and Lua and their
runtimes are compared in Figuare~\ref{fig:benchmarks_plot} and Figure~\ref{fig:benchmarks}.\footnote{
    The benchmarks and the scripts to run them can be found in the repository for this paper:
    \texttt{https://bitbucket.org/pypy/extradoc/src/ tip/talk/dls2012/benchmarks}
}
For benchmarks using larger Python applications the times are unaffected or
slightly improved by the loop optimization of this paper.
